A microservices based approach for city traffic simulation

### 2019-10-23 papers/traffic simulation/paper.tex
Outlines and notes completed.

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{abstract}
Simulating traffic in a city is a difficult task. Current paper is proposing a novel way using state of the art in distributed  microservices: orchestrating microservices. The desing is centered around two types of actors: a city simulation which keeps track of streets and cars densities. The other actor is the care which travels across the city.
\end{abstract}

\section{Introduction}

@@

\subsection{Inception}

@@

@@

@@

\subsection{Tools and programming languages}
\begin{itemize}
\item Go programming language
\item Docker
\item Docker compose
\item OpenSourceMap
\end{itemize}

@@

\subsection{Alternatives}

\subsection{Communication design}

@@

\subsection{}

>>>>

\documentclass[conference]{IEEEtran}
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{abstract}
Simulating traffic in a city is a difficult task. Current paper is proposing a novel way using state of the art in distributed systems: orchestrating microservices. The design is centered around two types of actors: a city simulation actor (a single instance of it) which keeps track of occupied streets and and their gradual occupation. The other actor type (multiple instances) is the car which travels across the city.
\end{abstract}

\section{Introduction}
Simulation of traffic in a given city has many benefits and applications.

(Terms definition)

@@

@@

\subsection{Implementation}

\section{Actors}

\subsection{City simulation actor}
(Reason)

(Types of data held: lines and densities)

(Future enhancements: integration into car actor for distributed consensus and data exchange)

\subsection{Car actor}
(Routing logic)

@@

\subsection{Implementation}

\subsection{Kubernetes}

@@

\subsection{Tools and programming languages}
\begin{itemize}
\item Go programming language
\item Docker
\item Docker compose
\item OpenSourceMap
\item Graphhopper
\item Web page choices (web page will become an actor)
\end{itemize}

@@

\subsection{Alternatives}
(Actor model and consacrated frameworks)

\subsection{Networking design}

@@

\section{Enhancements}
(Distributed database for multiple city simulators)

(More granular logic on actor behavior)
